Experience-Biased Symbolic Planning

### 2014-05-11 AAAI_AuthorKit/paper.tex
Theorem 3

By $\epsilon\epsilon^E$-consistency of the weighted heuristic $\epsilon h^E$, the E-graph search is complete and the path it finds is guaranteed to be at most $\epsilon \epsilon^E$-suboptimal. However, it makes no guarantee of improving the search time. Potential gains depend entirely on choosing a good small set of edges to call our E-graph. In our experiments we simply keep the previous solution path; different choices remain a topic of investigation for future research.

>>>>

\begin{thm}
Provided there exists a path from initial state $I$ to a goal state $S\supseteq G$, the experience-biased HSP algorithm finds a path which is at most $\epsilon\epsilon^E$-suboptimal.
\end{thm}

This follows directly from Theorems 1 and 2, since the weighted heuristic $\epsilon h^E$ is $\epsilon \epsilon^E$-consistent.
However, E-graphs make no guarantee of improving the search time. Indeed, biasing toward bad regions could trap the planner inside large local optima.
Potential gains depend entirely on choosing a good small set of edges to form our E-graph.
In our experiments, we simply keep the previous solution path; different choices remain a topic for future investigations.
